% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
% \documentclass[runningheads,dvipdfmx]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
\usepackage{multirow}
\usepackage{url}
%
\begin{document}
%
\title{Vertical Split Encoding: Enabling Larger N-Tuples for Stronger 2048 Play}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Shunsuke Terauchi \and %\orcidID{0000-1111-2222-3333}
Kiminori Matsuzaki\orcidID{0009-0003-4663-3292}}
%
\authorrunning{S.~Terauchi and K.~Matsuzaki}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Kochi University of Technology, Kami, Kochi 782--8502, Japan\\
\email{295141a@gs.kochi-tech.ac.jp}\\
\email{matsuzaki.Kiminori@kochi-tech.ac.jp}\\
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
N-tuple networks are a simple yet efficient approach to developing computer players for the game 2048,
but the tuple size has been limited to six or seven due to the memory constraints.
In this study, we break through this limitation by proposing a novel encoding method called Vertical Split Encoding (VSE).  VSE enables us to design N-tuple networks with 8-tuples or even 9-tuples.
We confirm through experiments that the performance degradation resulting from applying VSE is reasonably small, and that the newly developed 8-tuple networks significantly outperform the 6-tuple baseline, which was used in the state-of-the-art computer player, under the same experimental setting.

\keywords{2048 \and N-tuple networks \and Encoding.}
\end{abstract}
%
%
%
\input{introduction}
\input{2048}
\input{player}
\input{pre-experiments}
\input{NTuple}
\input{experiments}
% \input{consideration}
\input{conclusion}

\subsubsection{\ackname} This work was supported in part by JSPS KAKENHI Grant Number JP23K11383.

% \bibliographystyle{splncs04}
% \bibliography{ref}
\input{paper_bbl}
\end{document}

\begin{credits}
\subsubsection{\ackname} A bold run-in heading in small font size at the end of the paper is
used for general acknowledgments, for example: This study was funded
by X (grant number Y).

\subsubsection{\discintname}
It is now necessary to declare any competing interests or to specifically
state that the authors have no competing interests. Please place the
statement with a bold run-in heading in small font size beneath the
(optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
system, is used, then the disclaimer can be provided directly in the system.},
for example: The authors have no competing interests to declare that are
relevant to the content of this article. Or: Author A has received research
grants from Company W. Author B has received a speaker honorarium from
Company X and owns stock in Company Y. Author C is a member of committee Z.
\end{credits}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}, last accessed 2023/10/25
\end{thebibliography}

% LocalWords:  VSE Shunsuke Terauchi
