\begin{thebibliography}{10}
% \providecommand{\url}[1]{\texttt{#1}}
% \providecommand{\urlprefix}{URL }
% \providecommand{\doi}[1]{https://doi.org/#1}

\bibitem{ASOH22}
Antonoglou, I., Schrittwieser, J., Ozair, S., Hubert, T.K., Silver, D.:
  Planning in stochastic environments with a learned model. In: Proceedings of International
  Conference on Learning Representations (ICLR) (2022).

\bibitem{Buro98}
Buro, M.: From simple features to sophisticated evaluation functions. In:
  Proceedings of First International Conference on Computers and Games, CG'98.
  Lecture Notes in Computer Science, vol.~1558, pp. 126--145, Springer (1998).

\bibitem{CHHH24}
Chen, J.C., Hsu, T.Y., Hsu, C.M., Hsu, T.s.: Applying larger {N}-tuple networks
  to {EinStein} {W\"{u}rfelt} {Nicht!} In: Proceedings of the 2023 6th
  International Conference on Computational Intelligence and Intelligent
  Systems (CIIS '23). pp. 165--172, ACM (2024).

\bibitem{2048}
Cirulli, G.: 2048. \url{https://play2048.co/} (2014).

\bibitem{GuCW22}
Guei, H., Chen, L.P., Wu, I.C.: Optimistic temporal difference learning for
  2048. IEEE Transactions on Games, \textbf{14}(3), 478--487 (2022).

\bibitem{HsHs25}
Hsueh, W.L., Hsu, T.S.: An approximate solution of ``Einstein w\"urfelt
  nicht!''. In: Proceedings of 2025 IEEE Conference on Games (CoG), pp.~1--7 (2025).

\bibitem{HuQP18}
Huy, N.Q., Quoc, D.C., Phong, T.Q.: Selecting pattern shapes to build up an
  evaluation function for {Connect-6} game. In: Proceedings of the 4th
  International Conference on Virtual Reality, pp. 50--55, ACM (2018).

\bibitem{Jask18}
J\'{a}skowski, W.: Mastering 2048 with delayed temporal coherence learning,
  multi-stage weight promotion, redundant encoding and carousel shaping. IEEE
  Transactions on Computational Intelligence and AI in Games, \textbf{10}(1), 3--14 (2018).

\bibitem{Jask14}
Ja{\'s}kowski, W.: Systematic {N}-tuple networks for othello position
  evaluation. Journal of the International Computer Games Association,
  \textbf{37}(2),  85--96 (2014).

\bibitem{KGWW22}
Kao, C., Guei, H., Wu, T., Wu, I.: Gumbel MuZero for the game of 2048. In:
  Proceedings of International Conference on Technologies and Applications of Artificial
  Intelligence ({TAAI} 2022), pp. 42--47, {IEEE} (2022).

\bibitem{KuSM25}
Kuramitsu, H., Suzuki, K., Matsuzawa, T.: N-tuple network search in othello
  using genetic algorithms. Games, \textbf{16}(1) (2025).

\bibitem{Mats17}
Matsuzaki, K.: Developing 2048 player with backward temporal coherence learning
  and restart. In: Proceedings of Fifteenth International Conference on
  Advances in Computer Games (ACG2017). pp. 176--187 (2017)

\bibitem{Mats16}
Matsuzaki, K.: Systematic selection of n-tuple networks with consideration of
  interinfluence for game 2048. In: Proceedings of 2016 Conference on Technologies and
  Applications of Artificial Intelligence (TAAI), pp. 186--193 (2016).

\bibitem{Mats21}
Matsuzaki, K.: Developing value networks for game 2048 with reinforcement
  learning. Journal of Information Processing, \textbf{29},  336--346 (2021).

\bibitem{NgIL12}
Nguyen, H., Ikeda, K., Le, B.: Extracting important patterns for building
  state-action evaluation function in {Othello}. In: Proceedings of 2012 Conference on
  Technologies and Applications of Artificial Intelligence (TAAI 2012), pp. 278--283 (2012).

\bibitem{OkMa16}
Oka, K., Matsuzaki, K.: Systematic selection of n-tuple networks for 2048. In: Proceedings of
Computers and Games ({CG} 2016), Revised Selected Papers, Lecture Notes in Computer Science,
  vol. 10068, pp. 81--92. Springer (2016).

\bibitem{SzJa14}
Szubert, M., Ja\'{s}kowski, W.: Temporal difference learning of {N}-tuple
  networks for the game 2048. In: Proceedings of 2014 IEEE Conference on Computational
  Intelligence and Games, pp.~1--8 (2014).

\bibitem{TeKM23}
Terauchi, S., Kubota, T., Matsuzaki, K.: Using strongly solved {Mini2048} to
  analyze players with {N-tuple} networks. In: Proceedings of International Conference on
  Technologies and Applications of Artificial Intelligence ({TAAI} 2023) (2023).

\bibitem{TeMa25}
Terauchi, S., Matsuzaki, K.: Relationship between the size of {N}-tuple network
  and learning performance: Experiments and evaluation using mini2048 (in
  Japanese). IPSJ SIG Technical Reports {2025-GI-55}, pp.~1--9 (2025).

\bibitem{ThKK12}
Thill, M., Koch, P., Konen, W.: Reinforcement learning with {N}-tuples on the
  game {Connect-4}. In: Proceedings of the 12th International Conference on
  Parallel Problem Solving from Nature --- Volume Part I, pp. 184--194,
  Springer-Verlag (2012).

\bibitem{WaMa25}
Wang, W., Matsuzaki, K.: Refining evaluation functions for game 2048 by
  extended temporal difference learning. IEEE Transactions on Games, pp. 1--11
  (2025), available as an early access article.

\bibitem{YaKN22}
Yamashita, S., Kaneko, T., Nakayashiki, T.: Strongly solving 2048 on 3 × 3
  board and performance evaluation of reinforcement learning agents. In:
  Proceedings of the Game Programming Workshop 2022. pp.~1--8 (2022), in
  Japanese.

\bibitem{YWHC16}
Yeh, K.H., Wu, I.C., Hsueh, C.H., Chang, C.C., Liang, C.C., Chiang, H.:
  Multi-stage temporal difference learning for 2048-like games. IEEE
  Transactions on Computational Intelligence and AI in Games, \textbf{9}(4),
  369--380 (2016).

\bibitem{Zhou19}
Zhou, Y.: From {AlphaGo} Zero to 2048. Workshop on Deep Reinforcement Learning
  for Knowledge Discovery (DRL4KDD '19), Available on
  \url{http://www.cse.msu.edu/~zhaoxi35/DRL4KDD/2.pdf} (2019).

\end{thebibliography}
